Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-31 manuscript/manuscript.Rmd
textbox and conceptual fig positioning
revised abstract

abstract: |
  Existing methods for optimal control struggle to deal with the
  complexity commonly encountered in real-world systems, including
  dimensionality, process error, model bias and heterogeneity.  Instead
  of tackling these complexities directly, researchers have typically
  sought to find exact optimal solutions to simplified models of the
  processes in question. When is the optimal solution to a very
  approximate, stylized model better than an approximate solution to a
  more accurate model? This question has largely gone unanswered owing
  to the difficulty of finding even approximate solutions in the case of
  complex models.  Our approach draws on recent algorithmic and
  computational advances in deep reinforcement learning. These methods
  have hitherto focused on problems in games or robotic mechanics, which
  operate under precisely known rules. We demonstrate the ability for
  novel algorithms using deep neural networks to successfully
  approximate such solutions (the ‘‘policy function’’ or control rule)
  without knowing or ever attempting to infer a model for the process
  itself. This powerful new technique lets us finally begin to answer
  the question. We showcase this approach by applying it to the control
  of a highly non-linear three-variable model for a fishery. Here, the
  reinforcement learning agent discovers an effective simplification of
  the problem to obtain a simple, interpretable control rule. Moreover,
  the policy obtained is both more profitable and more sustainable than
  any constant mortality policy---the standard family of policies considered
  in fishery management.

>>>>

abstract: |
  Existing methods for optimal control struggle to deal with the
  complexity commonly encountered in real-world systems, including
  dimensionality, process error, model bias and data heterogeneity.
  Instead of tackling these system complexities directly, researchers 
  have typically sought to simplify models to fit optimal control 
  methods. But when is the optimal solution to an approximate, stylized 
  model better than an approximate solution to a more accurate model? 
  While this question has largely gone unanswered owing to the 
  difficulty of finding even approximate solutions for complex models, 
  recent algorithmic and computational advances in deep reinforcement 
  learning (DRL) might finally allow us to address these questions. DRL 
  methods have to date been applied primarily in the context of games 
  or robotic mechanics, which operate under precisely known rules. Here, 
  we demonstrate the ability for DRL algorithms using deep neural networks 
  to successfully approximate solutions (the ‘‘policy function’’ or control 
  rule) in a non-linear three-variable model for a fishery without knowing 
  or ever attempting to infer a model for the process itself. We find that 
  the reinforcement learning agent discovers an effective simplification of
  the problem to obtain an interpretable control rule. We show that the 
  policy obtained with DRL is both more profitable and more sustainable 
  than any constant mortality policy---the standard family of policies 
  considered in fishery management.
